Rising from the Ashes: How the Milky Way Got Its Scars

### 2024-04-20 paper/ms.tex
Update abstract, title

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{newtxtext,newtxmath}
\usepackage{hyperref}

@@

\newcommand{\Msun}{\ensuremath{M_{\odot}}}
\newcommand{\Gyr}{\ensuremath{\textrm{Gyr}}}
\newcommand{\Myr}{\ensuremath{\textrm{Myr}}}
\newcommand{\yr}{\ensuremath{\textrm{yr}}}
\newcommand{\kpc}{\ensuremath{\textrm{kpc}}}
\newcommand{\pc}{\ensuremath{\textrm{pc}}}
\newcommand{\tocite}{\textcolor{blue}{cite}}
\newcommand{\FeH}{\ensuremath{[\textrm{Fe}/\textrm{H}]}}
\newcommand{\MgFe}{\ensuremath{[\textrm{Mg}/\textrm{Fe}]}}
\newcommand{\alphaFe}{\ensuremath{[\alpha/\textrm{Fe}]}}

@@

\shorttitle{The CGM of Merging Galaxies}
\shortauthors{Beane et al.}

@@

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
  Stars are thought to inherit the elemental abundances of their birth cloud and, for the most part, to not change their surface abundances over time. Stellar surface abdundances are, therefore, a promising avenue to probe the time evolution of the abundance distribution of the Galaxy's gas phase. A particularly useful compression of the high-dimensional abundance plane is to consider the distribution of $\alpha$ elements for a given total metallicity, usually tracked by iron. It is well-known that this distribution of $\alpha$ is bimodal, for which there is a growing consensus that the low-$\alpha$ sequence diverges from the high-$\alpha$ sequence as a result of a merger. In this work, we propose the phoenix hypothesis: the bimodality is caused by a brief ($\sim300\,\Myr$) period of quiescent star formation, possibly preceded by a starburst. The bimodality is a natural consequence of stellar populations enriching the Galactic disk during a period in which no stars are forming. Our proposal is consistent with a merger, but it is agnostic to the exact mechanism by which the quiescent period arises. Our proposal predicts no overlap in age between the high- and low-$\alpha$ sequence at a given birth radius.
\end{abstract}

>>>>

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{newtxtext,newtxmath}
\usepackage{hyperref}
\usepackage{gensymb}

@@

\newcommand{\Msun}{\ensuremath{M_{\odot}}}
\newcommand{\Gyr}{\ensuremath{\textrm{Gyr}}}
\newcommand{\Myr}{\ensuremath{\textrm{Myr}}}
\newcommand{\yr}{\ensuremath{\textrm{yr}}}
\newcommand{\kpc}{\ensuremath{\textrm{kpc}}}
\newcommand{\pc}{\ensuremath{\textrm{pc}}}
\newcommand{\tocite}{\textcolor{blue}{cite}}
\newcommand{\FeH}{\ensuremath{[\textrm{Fe}/\textrm{H}]}}
\newcommand{\MgFe}{\ensuremath{[\textrm{Mg}/\textrm{Fe}]}}
\newcommand{\alphaFe}{\ensuremath{[\alpha/\textrm{Fe}]}}
\newcommand{\tform}{\ensuremath{t_{\textrm{form}}}}
\newcommand{\dex}{\ensuremath{\textrm{dex}}}

@@

\shorttitle{The Milky Way's Phoenix Phase}
\shortauthors{Beane et al.}

@@

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
  Stars are thought to inherit the elemental abundances of their birth cloud and, for the most part, to not change their surface abundances over time. Stellar surface abdundances are, therefore, a promising avenue to probe the time evolution of the abundance distribution of the Galaxy's gas phase. A particularly useful compression of the high-dimensional abundance plane is to consider the distribution of $\alpha$ elements for a given total metallicity, usually tracked by iron. It is well-known that this distribution of $\alpha$ is bimodal, for which there is a growing consensus that the low-$\alpha$ sequence diverges from the high-$\alpha$ sequence as a result of a merger. The general idea is that fresh, pristine gas from the merger causes a sudden change in the abundance structure of the disk, such that the gas spends relatively little time in the valley of bimodality. However, we argue that it is also possible that when the Galaxy's gas phase was in the valley that it was quiescent. This relaxes the necessity for a rapid abundance transition. A preceding starburst, which may cause the quiescent phase, would also be a culprit in the abundance transition.

  In this work, we propose the phoenix hypothesis: the bimodality is caused by a brief ($\sim300\,\Myr$) period of quiescent star formation, possibly preceded by a starburst. The bimodality is a natural consequence of stellar populations enriching the Galactic disk during a period in which no stars are forming. Our proposal is consistent with a merger, but it is agnostic to the exact mechanism by which the quiescent period arises. Our proposal predicts no overlap in age between the high- and low-$\alpha$ sequence at a given birth radius.
\end{abstract}
